Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-08-13 paper/paper.tex
Proof of Prop1

\begin{proposition}
    Let $p$ be a vertex of $P$ and $t$ a vertex in $T$. For both non-induced and induced
    subgraph-except-$k$ isomorphisms, if $p \prescript{}{k}{\mapsto} t$ then
    $\operatorname{deg}(p) \le \operatorname{deg}(t) + k$.
\end{proposition}

>>>>

\begin{proposition}
    Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
    subgraph-except-$k$ isomorphisms, if $p \prescript{}{k}{\mapsto} t$ then
    $\operatorname{deg}(p) \le \operatorname{deg}(t) + k$.
\end{proposition}
\begin{proof}
Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$. Then by the definition of subgraph isomorphisms, $\operatorname{deg}(p) \le \operatorname{deg}(t)$. Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$. Then
\[
\operatorname{deg}_{P}(p)-k \le \operatorname{deg}_{P'}(p) \le \operatorname{deg}_{P}(p) \le \operatorname{deg}(t).
\]
\end{proof}
